Basics of Hardware Cache Optimization

### 2017-06-23 tex/basic-concepts/lines.tex
Add more slides, tweak stuff

% XXX: hacks!  Explicit placement specifier without `t` (top) to prevent the figure from
% interrupting the source code listing.
\begin{figure}%[hbp]
   \centering
   \begin{tikzpicture}
      \datavisualization
      [scientific axes=clean,
       x axis={logarithmic,
               ticks={major at={1, 2, 4, 8 as \textbf{8}, 16, 64, 256, 1024},
                      minor at={32, 128, 512}},
               grid={at=8},
               label={Step Size}, length=0.8\textwidth},
       y axis={logarithmic,
               % ticks={major={at={4, 16, 64, 256}}, minor={at={8, 32, 128}}},
               % ticks={major={at={6, 12, 24, 48, 92, 184}}},
               ticks={major at={10, 20, 40, 80, 160, 320}},
               grid=at ticks,
               label={Processor Time (ms)}, length=6cm},
       visualize as scatter,
       scatter={style={mark=*, mark options={scale=.65}}}]
         % See <https://tex.stackexchange.com/q/198323>.
         data [read from file=line-size/line-size.csv, separator=\space];
   \end{tikzpicture}
   \caption{Processor Times for Running \Cref{lst:line-size}}
   \label{fig:line-size}
\end{figure}

% vim: tw=90 sts=-1 sw=3 et fdm=marker

>>>>

\begin{figure}
   \centering
   \input{tex/graphics/line-size-plot}
   \caption{Processor Times for Running \Cref{lst:line-size}}
   \label{fig:line-size}
\end{figure}

% vim: ft=tex tw=90 sts=-1 sw=3 et fdm=marker
